\subsection{Rationale}\label{rationale}

We wanted to cover the Linux Foundation due to all of us having
extensive knowledge using Linux. We wanted to know more about what they
do due to our use of Linux. We all kind of chose at the same time and
all agreed just because we all wanted to know more.

\section{Organizational Details}\label{organizational-details}

\begin{center}\rule{3in}{0.4pt}\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Oregon-based nonprofit mutual benefit corporation
\item
  Founded 2000, Incorporated August 9th, 2007
\item
  TODO: Info on founders is \textbf{\emph{very}} hard to find

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    I've emailed the Foundation asking for information
  \end{itemize}
\end{itemize}

\begin{center}\rule{3in}{0.4pt}\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Private company
\item
  No acquisitions
\item
  \textbf{``No investments''}
\item
  21 Leaders
\item
  HQ in San Francisco
\item
  Also offices in Japan and Korea
\end{itemize}

\begin{center}\rule{3in}{0.4pt}\end{center}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{http://linuxfoundation.org}{linuxfoundation.org}
\item
  \href{http://en.wikipedia.org/wiki/Linux_Foundation}{Linux Foundation
  (wikipedia)}
\item
  Yearly
  \href{http://www.linuxfoundation.org/publications/linux-foundation}{Linux
  Job Reports}
\end{itemize}

\section{Communications}\label{communications}

\subsection{Social media}\label{social-media}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{https://twitter.com/linuxfoundation}{Twitter}: 167K Followers
\item
  \href{https://plus.google.com/+LinuxfoundationOrg/posts}{Google+}: 30K
  Followers
\item
  \href{https://www.facebook.com/TheLinuxFoundation}{Facebook}: 340K
  Likes
\item
  \href{https://www.youtube.com/user/TheLinuxFoundation}{Youtube}: 43K
  Subscribers
\end{itemize}

\subsection{Communications channels}\label{communications-channels}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The Linux Foundation has a News and Blogs page here with news and
  other info that they would like to distribute.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    \url{http://www.linuxfoundation.org/news-media/news}
  \end{itemize}
\item
  All Linux Foundation announcements can be seen here specifically.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    \url{http://www.linuxfoundation.org/news-media/announcements}
  \end{itemize}
\item
  They also keep a list of infographics.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    \url{http://www.linuxfoundation.org/news-media/infographics}
  \end{itemize}
\item
  This is a list of all publications the Linux Foundation have,
  including open source compliance and workshops.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    \url{http://www.linuxfoundation.org/publications}
  \end{itemize}
\item
  They also operate a monthly newsletter.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    \url{http://www.linuxfoundation.org/about/stay-connected/newsletter}
  \end{itemize}
\end{itemize}

\subsection{Conference Participation}\label{conference-participation}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The Linux Foundation hosts \textbf{a lot} of conferences. They have 15
  conferences planned from March to the end of the year.
\item
  They also have partner conferences too where they team up with other
  companies to host conferences.

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    There are at least 12 until the end of the year.
  \end{itemize}
\item
  They cover a variety of topics, all of which relate to Linux somehow.
\item
  Some conferences are colocated on the same date and location so that
  smaller conferences can be booked with larger conferences.
\item
  \href{http://events.linuxfoundation.org/events/android-builders-summit}{Android
  Builders Summit} on March 23rd
\item
  \href{http://events.linuxfoundation.org/events/embedded-linux-conference}{Embedded
  Linux Conference} on March 23rd
\item
  \href{http://events.linuxfoundation.org/events/apachecon-north-america}{ApacheCon}
  on April 13th
\item
  \href{http://events.linuxfoundation.org/events/kvm-forum}{KVMForum} on
  August 19th
\item
  \href{http://events.linuxfoundation.org/events/linux-kernel-summit}{Annual
  Linux Kernel Summit} on October 26th
\end{itemize}

\section{Community Architecture}\label{community-architecture}

\subsection{Communication Channels}\label{communication-channels}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Linux Standard Base IRC: \#lsb@irc.freenode.net
\item
  \href{http://kernel.org}{kernel.org} (Canonical Repository)
\item
  \href{https://github.com/torvalds/linux}{Linux Kernel GitHub}
\item
  \href{https://lkml.org/}{Linux Kernel Mailing List Archive}
\end{itemize}

\subsection{Membership}\label{membership}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Anyone can join
\item
  Fee based
\item
  Corporate
\item
  Individual
\end{itemize}

\subsection{Corporate Members}\label{corporate-members}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Fujitsu
\item
  HP
\item
  IBM
\item
  Intel
\item
  \href{http://www.linuxfoundation.org/about/members}{and more}
\item
  \href{http://www.linuxfoundation.org/about/board-members}{About the
  Board of Directors}
\end{itemize}

\subsection{About}\label{about}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Distribute the Linux kernel and other Open Source software to the
  public without charge.
\item
  Initial Git commit
  \href{https://github.com/torvalds/linux/commit/1da177e4c3f41524e886b7f1b8a0c1fc7321cac2}{Linux-2.6.12-rc2}
  April 16, 2005
\item
  Patches are approved by kernel module subcommitees
\item
  BDFL = \href{http://en.wikipedia.org/wiki/Linus_Torvalds}{Linus
  Torvalds}
\end{itemize}

\subsection{Community Participation}\label{community-participation}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Participation is increasing:
  \href{http://www.zdnet.com/article/linus-torvalds-still-wants-the-linux-desktop/}{YoTLD}
\item
  Passes Raptor Test (Board of Directors, set process to replace)
\item
  Passes Bus Test (with due chaos)
\item
  \href{http://kernelnewbies.org/}{kernelnewbies.org}
\end{itemize}

\section{Technology/Product}\label{technologyproduct}

\subsection{Linux}\label{linux}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  The Linux Foundation is centered around promoting, standardizing, and
  protecting Linux.
\item
  Linux is an open source operating system used on tons of platforms
  ranging from small embedded devices to large clusters of servers.
\item
  Anyone needing a non-realtime operating system kernel could benefit
  from using Linux.
\item
  Massive amounts of companies have a stake in the Linux kernel as well
  as the Linux Foundation. There are 185 corporate members of the Linux
  Foundation.
\item
  One of the main reasons Linux became so popular was that it was open
  sourced and GPL licensed, which wasn't common when it was made.
\end{itemize}
